The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2019-06-19 razzo-introduction.tex
Folded in a readable way

Current phylogenetic tools assume that only a single speciation event can occur at any given time.
While this assumption has been proved to be useful to construct a wide variety of successful models (e.g \cite{Maddison2007biSSE}, \cite{Valente2015}, \cite{etienne2012diversity}, \cite{etienne2014estimating}), they disallow for environmental changes that trigger speciations in multiple clades at a same point in time.

@@

The (constant-rate) birth-death (BD) model embodies the common assumption that only a single speciation event can occur at any given time.
The multiple-birth-death (MBD) model relaxes this assumption allowing, in addition to standard BD events, also events in which large-scale environmental changes lead to speciation bursts.
Such hypothesis can be useful to better understand the history of systems of particular interests for evolutionary biologists, such as the  diversification of cichlid fish in the African Great Lakes (Malawi, Tanganyika and Victoria), where water level fluctuations are thought to play an important role in promoting diversification (\citep{verheyen1996mitochondrial}, \citep{sturmbauer2001lake}, \citep{janzen2016}, \citep{janzen2017}).

>>>>

Current phylogenetic tools assume that only a single speciation event can occur 
at any given time.
While this assumption has been proved to be useful to construct a wide 
variety of successful models (e.g \cite{Maddison2007biSSE}, 
\cite{Valente2015}, \cite{etienne2012diversity}, \cite{etienne2014estimating}), 
they disallow for environment
al changes that trigger speciations in multiple clades at a same point in time.

@@

The (constant-rate) birth-death (BD) model embodies the common assumption that 
only a single speciation event can occur at any given time. The 
multiple-birth-death (MBD) model relaxes this assumption allowing, in additi
on to standard BD events, also events in which large-scale environmental 
changes lead to speciation bursts.
Such hypothesis can be useful to better understand the history of systems of 
particular interests for evolutionary biologists, such as the 
diversification of cichlid fish in the African Great Lakes (Malawi, 
Tanganyika and Victoria), where 
water level fluctuations are thought to play an important role in promoting 
diversification (\citep{verheyen1996mitochondrial}, \citep{sturmbauer2001lake}, 
\citep{janzen2016}, \citep{janzen2017}).
